Automatic Extraction of JavaScript Formal Semantics from ECMAScript Specifications

### 2019-07-25 icse/related.tex
Added related works

\subsection{Parser Generation}
\subsection{Automatic Semantics Extraction}
\begin{itemize}
  \item Automatic Model Generation from Documentation for Java API Functions (ICSE'16)
\end{itemize}

\subsection{Formal Semantics of JavaScript}
\begin{itemize}
  \item KJS: A complete formal semantics of JavaScript (PLDI'15)
  \item The Essence of JavaScript (ECOOP'10)
\end{itemize}

% A Trusted Mechanised JavaScript Specification (POPL'14)

>>>>

\subsection{Parser Generation}
\begin{itemize}
  \item Packrat parsing:: simple, powerful, lazy, linear time, functional pearl (ICFP'02)~\cite{packrat}
\end{itemize}

\subsection{Automatic Semantics Extraction}
\begin{itemize}
  \item Automatic Model Generation from Documentation for Java API Functions (ICSE'16)~\cite{javadoc}
\end{itemize}

\subsection{Formal Semantics of JavaScript}
\begin{itemize}
  \item KJS: A complete formal semantics of JavaScript (PLDI'15)~\cite{kjs}
  \item The Essence of JavaScript (ECOOP'10)~\cite{lambdajs}
  \item A Trusted Mechanised JavaScript Specification (POPL'14)~\cite{jscert}
\end{itemize}
